Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-15 ForegroundSimulations/ms.tex
Minor adjustment in section 5.2.1
From 1caedff (fgsim):
====================

In ms.tex,

(*) Minor adjustment in section 5.2.1

For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on a 14.6~m baseline in equation~\ref{eqn:attenuation}. Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted). These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections. It implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.

@@

The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections. This depends sensitively on the chosen $k_\parallel$ modes. For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$. Measurements by \citet{pat16} for HERA dish-feed assembly show that the return losses lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.

>>>>

For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on a 14.6~m baseline in equation~\ref{eqn:attenuation}. Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted). These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays. These reflections are primarily caused in the dish-feed assembly and to some extent in other subsystems not accounted for. It implies that if these reflections are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.

@@

The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections. This depends sensitively on the chosen $k_\parallel$ modes. For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$. Measurements by \citet{pat16} show that the return losses for HERA lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
